Evidence of Magnetic Saturation from Stellar Flare Rates

### 2023-10-30 src/tex/ms.tex
caption + color bar

\begin{figure}[ht!]
    \script{yp_rates.py}
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/yp_rates.pdf}
        \caption{
            Comparison of flare rates from young planet host stars with respect to
            a comparable sample with respect to age [Myr] and $T_\textrm{eff}$ [K].
        }
        \label{fig:yp_rates}
    \end{centering}
\end{figure}

\begin{deluxetable}{l r r r}[!ht]
\tabletypesize{\footnotesize}
\tablecaption{Young Planet Host Flare Rates\label{tab:yprates}}
\tablehead{
\colhead{Host Name} & \colhead{Age} & \colhead{Flare Rate} & \colhead{Comp. Sample} \\
 & \colhead{[Myr]} & \colhead{[day$^{-1}$]} & \colhead{Flare Rate [day$^{-1}$]}
}
\startdata
TOI 1227 &  $11 \pm 2$ &  0.008  & $0.119_{-0.046}^{+0.148}$ \\
HIP 67522 & $17 \pm 2$ &  0.169  & $0.046_{-0.020}^{+0.069}$ \\
AU Mic & $22 \pm 3$ &  2.218  & $0.133_{-0.046}^{+0.171}$ \\
V1298 Tau & $23 \pm 4$ &  0.022  & $0.074_{-0.033}^{+0.091}$ \\
HD 109833 & $27 \pm 3$ & 0.000  & $0.046_{-0.020}^{+0.070}$ \\
KOI-7913 & $36 \pm 10$ &  0.031  & $0.134_{-0.045}^{+0.162}$ \\
KOI-7368 & $36 \pm 10$ &  0.029  & $0.064_{-0.030}^{+0.087}$ \\
DS Tuc & $45 \pm 4$ &  0.420  & $0.056_{-0.024}^{+0.078}$ \\
TOI 942 & $50_{-20}^{+30} $ &  0.040  & $0.086_{-0.038}^{+0.117}$ \\
TOI 451 & $120 \pm 10$ &  0.128  & $0.071_{-0.029}^{+0.085}$ \\
HIP 94235 & $133_{-20}^{+15}$ &  0.020  & $0.051_{-0.017}^{+0.079}$ \\
TOI 1860 & $133 \pm 26$ &  0.008  & $0.067_{-0.025}^{+0.086}$ \\
TOI 1807 & $180 ± 40$ &  0.013  & $0.060_{-0.022}^{+0.085}$ \\
HD 18599 & $200_{-70}^{+200} $ & 0.000 & $0.025_{-0.015}^{+0.044}$ \\
TOI 2076 & $204 \pm 50$ & 0.000 & $0.092_{-0.045}^{+0.091}$ \\
HD 110082 & $250_{-70}^{+50} $ & 0.000 & $0.047_{-0.020}^{+0.067}$ \\
\enddata
\end{deluxetable}

>>>>

\begin{figure}[ht!]
    \script{yp_rates.py}
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/yp_rates.pdf}
        \caption{
            Comparison of flare rates from young planet host stars with respect to
            a comparable sample with respect to age [Myr] and $T_\textrm{eff}$ [K].
            Circles represent the flare rate of the host star (name along the x-axis);
            vertical bars represent the lower 16\textsuperscript{th} and upper
            84\textsuperscript{th} percentiles for the comparable sample. The majority
            of young planet hosting stars have flare rates towards the lower end of the
            comparable sample's distribution. A handful of hosts have more flares, including
            HIP 67522, AU Mic, DS Tuc A, and TOI 451. We find no correlation between
            age or $T_\textrm{eff}$ that may result in young planet hosts having more or fewer
            flares than a larger comparable sample. The measured flare rates are presented in
            Table~\ref{tab:yp_rates}.
        }
        \label{fig:yp_rates}
    \end{centering}
\end{figure}

\begin{deluxetable}{l r r r}[!ht]
\tabletypesize{\footnotesize}
\tablecaption{Young Planet Host Flare Rates\label{tab:yp_rates}}
\tablehead{
\colhead{Host Name} & \colhead{Age} & \colhead{Flare Rate} & \colhead{Comp. Sample} \\
 & \colhead{[Myr]} & \colhead{[day$^{-1}$]} & \colhead{Flare Rate [day$^{-1}$]}
}
\startdata
TOI 1227 &  $11 \pm 2$ &  0.008  & $0.119_{-0.046}^{+0.148}$ \\
HIP 67522 & $17 \pm 2$ &  0.169  & $0.046_{-0.020}^{+0.069}$ \\
AU Mic & $22 \pm 3$ &  2.218  & $0.133_{-0.046}^{+0.171}$ \\
V1298 Tau & $23 \pm 4$ &  0.022  & $0.074_{-0.033}^{+0.091}$ \\
HD 109833 & $27 \pm 3$ & 0.000  & $0.046_{-0.020}^{+0.070}$ \\
KOI-7913 & $36 \pm 10$ &  0.031  & $0.134_{-0.045}^{+0.162}$ \\
KOI-7368 & $36 \pm 10$ &  0.029  & $0.064_{-0.030}^{+0.087}$ \\
DS Tuc & $45 \pm 4$ &  0.420  & $0.056_{-0.024}^{+0.078}$ \\
TOI 942 & $50_{-20}^{+30} $ &  0.040  & $0.086_{-0.038}^{+0.117}$ \\
TOI 451 & $120 \pm 10$ &  0.128  & $0.071_{-0.029}^{+0.085}$ \\
HIP 94235 & $133_{-20}^{+15}$ &  0.020  & $0.051_{-0.017}^{+0.079}$ \\
TOI 1860 & $133 \pm 26$ &  0.008  & $0.067_{-0.025}^{+0.086}$ \\
TOI 1807 & $180 ± 40$ &  0.013  & $0.060_{-0.022}^{+0.085}$ \\
HD 18599 & $200_{-70}^{+200} $ & 0.000 & $0.025_{-0.015}^{+0.044}$ \\
TOI 2076 & $204 \pm 50$ & 0.000 & $0.092_{-0.045}^{+0.091}$ \\
HD 110082 & $250_{-70}^{+50} $ & 0.000 & $0.047_{-0.020}^{+0.067}$ \\
\enddata
\end{deluxetable}
